### 2015-05-14 evaluation.tex
A couple of changes

\noindent\textbf{Race-Checking }
%
Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs reported by \whoop (\#Racy Pairs); number of racy memory regions identified by \whoop (\#Racy MRs); and number of races discovered by \corral using a context-switch bound (csb) of 2 (\#Races Found). Note that we did not discover any new races with a higher csb; this might mean that races in our benchmarks require only one or two context-switches to manifest, or that \corral hit its bounds before discovering a deeper bug. Furthermore, \corral did not discover any races that \whoop did not already report, giving us extra confidence in the implementation of \whoop.

>>>>

\noindent\textbf{Race-Checking }
%
Table~\ref{tab:stats} presents statistics for all our benchmarks: lines of code (LoC); number of entry point pairs (\#Pairs); number of SMACK memory regions (\#MRs); number of racy pairs reported by \whoop (\#Racy Pairs); number of racy memory regions identified by \whoop (\#Racy MRs); and number of races discovered by \corral using a context-switch bound (csb) of 2 (\#Races Found). Using a higher csb did not uncover any further races; this might mean that races in our benchmarks require only one or two context-switches to manifest, or that \corral hit its bounds before discovering a deeper bug. \corral did not discover any races that \whoop did not already report.  This is expected, as \whoop aims for soundness, and increases our confidence in the implementation of \whoop.

### 2015-05-14 related.tex
A couple of changes

Statically analyzing concurrent programs for races is a promising alternative to dynamic analyzers, which typically rely on a (controlled) scheduler for exploring execution paths, and thus can face code coverage issues~\cite{musuvathi2008finding}. Warlock~\cite{sterling1993warlock} and LockLint~\cite{oracle2010locklint} are notable examples of static race analyzers. However, both tools have limited applicability, as they heavily rely on user annotations. \textsc{Whoop}, on the other hand, does not require any source code modifications, and thus can be applied with minimal effort.

@@

Our work is not the first to exploit static analysis for achieving efficient race-checking. Prior work includes: \cite{choi2002efficient}, which combined static analysis, optimized instrumentation and runtime access caching to speedup dynamic data race detection; \cite{kahlon2007fast}, which combined a divide-and-conquer strategy that partitions all pointers of a program that cannot alias in disjoint sets and function summarization to achieve a scalable context-sensitive alias analysis for data races; \cite{kahlon2009semantic}, which used abstract interpretation to achieve a sound partial-order reduction on the set of thread interleavings and statically reduce the number of false data race warnings; and \cite{das2015section}, which combined inter-procedural pointer analysis with verifiable user annotations to split programs into disjoint sections, based on non-communicating accesses of shared data, and eliminate redundant checks during dynamic race detection.

>>>>

Statically race analysis is a promising alternative to dynamic techniques, which restrict analysis to the schedule chosen by a (possibly controlled) scheduler, providing limited coverage~\cite{musuvathi2008finding}. Warlock~\cite{sterling1993warlock} and LockLint~\cite{oracle2010locklint} are notable static race analyzers.  In comparison to \whoop, these tools rely heavily on user annotations.

@@

Prior works on static race checking include: \cite{choi2002efficient}, which combined static analysis, optimized instrumentation and runtime access caching to speedup dynamic data race detection; \cite{kahlon2007fast}, which combined a divide-and-conquer strategy that partitions all pointers of a program that cannot alias in disjoint sets and function summarization to achieve a scalable context-sensitive alias analysis for data races; \cite{kahlon2009semantic}, which used abstract interpretation to achieve a sound partial-order reduction on the set of thread interleavings and statically reduce the number of false data race warnings; and \cite{das2015section}, which combined inter-procedural pointer analysis with verifiable user annotations to split programs into disjoint sections, based on non-communicating accesses of shared data, and eliminate redundant checks during dynamic race detection.
